A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-29 pilot-publication/manuscript.Rmd
Start working on patient participants outcomes

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table 
\@ref(tab:sample-characteristics). Overall, the
number of females were X (X%), the median age was X (IQR X), and the
median ISS was X (IQR X). A total of X (X%) patients had the primary
outcome of mortality at 30 days after arrival to the emergency
department.

@@

## Patient Participant Outcomes
In the post training period, a total of X (X%) patients in the ATLS
arm had the primary outcome, compared to X (X%) patients in the PTC
arm, and X (X%) patients in the standard care arm. The differences
between the arms were X (95% CI X - X) between the ATLS and PTC arms,
X (95% CI X - X) between the ATLS and standard care arms, and X (95%
CI X - X) between the PTC and standard care arms. The change from
baseline for the primary outcome was X in the ATLS arm, X in the PTC
arm, and X in the standard care arm. The differences between changes
from baseline were X (95% CI X - X) between the ATLS and PTC arms, X
(95% CI X - X) between the ATLS and standard care arms, and X (95% CI
X - X) between the PTC and standard care arms. Table X shows
differences in the primary outcome between trial arms with 75, 85, and
95% CIs. Differences in secondary outcomes between trial arms and
subgroups are available as Supplementary material X.

@@

>>>>

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r n.females` (`r p.females`%), the median age was `r median.age`
years (IQR `r iqr.age`), and the median ISS was X (IQR X). A total of
`r n.m30d` (`r p.m30d`%) patients had the primary outcome of mortality
at 30 days after arrival to the emergency department.

@@

## Patient Participant Outcomes
In the post training period, a total of `r n.m30d.atls` 
(`r p.m30d.atls`%) patients in the ATLS arm had the primary outcome,
compared to `r n.m30d.ptc` (`r p.m30d.ptc`%) patients in the PTC arm, 
and `r n.m30d.control` (`r p.m30d.control`%) patients in the standard
care arm. The absolute risk difference between the ATLS and PTC arm 
was X (95% CI X - X), between the ATLS and standard care arms X 
(95% CI X - X), and between the PTC and standard care arms X 
(95% CI X - X).

The change from baseline for the primary outcome was X in the ATLS
arm, X in the PTC arm, and X in the standard care arm. The differences
between changes from baseline were X (95% CI X - X) between the ATLS
and PTC arms, X (95% CI X - X) between the ATLS and standard care
arms, and X (95% CI X - X) between the PTC and standard care
arms. Table X shows differences in the primary outcome between trial
arms with 75, 85, and 95% CIs.

Differences in secondary outcomes between trial arms and subgroups are
available as Supplementary material X.

@@

<!-- Consider discussing waiver of informed consent for initial 
data collection -->
